ICM testing

### 2023-06-22 Scripts/ASR_stocks.Rmd
End of MAESTRO update
Still trying to sort out Esmarkii and Cod tuning shit.  Also still thinking about the correct ages to use for the VPA time sereis.  I think it is right now, but still needs more thought.  Gettnig close, but not quite there for the tuning stuff

```{r, load-stuff,echo=F, message=F, warning=F, fig.width=6, fig.height=4}
# OK, so using the ICES assessments here's what we get for North Sea cod.
library(readxl)
library(tidyverse)
library(rio)
library(ggthemes)
library(cowplot)

source("D:/Github/ICM/Scripts/functions/backwards_sim.R")
source("D:/Github/ICM/Scripts/functions/tuning_sim.R")

# Choose 5 ICES stocks that we have the necessary data for
#ASR <- read_xlsx("../Data/ASR_2018.xlsx", sheet = "ICES")
ASR1 <- read.csv("D:/Github/ICM/Data/ICM_data_NE_atlantic_stocks.csv")
ASR <- read.csv("D:/Github/ICM/Data/ICM_data_NW_atlantic_stocks.csv")

@@

  age.mat <- ASR_sub %>% dplyr::filter(type=="AM") %>% dplyr::rename(AM=value) %>% dplyr::select(-type)
  nat.mort <-  ASR_sub %>% dplyr::filter(type=="NM") %>% dplyr::rename(NM=value) %>% dplyr::select(-type)
  abund <- ASR_sub %>% dplyr::filter(type=="Num") %>% dplyr::rename(Num=value) %>% dplyr::select(-type)
  weight.age <- ASR_sub %>% dplyr::filter(type=="WA") %>% dplyr::rename(WA=value) %>% dplyr::select(-type)
  removals <- ASR_sub %>% dplyr::filter(type=="Catch") %>% dplyr::rename(Catch=value) %>% dplyr::select(-type)

@@

  data$available <- apply(is.na(data[, c("AM", "Num", "WA")]), 1, function(x) all(!x==T))
  data <- data[data$available==T,]

@@

save(years.tmp,pnm.tmp,waa.tmp,ages.tmp,rem.tmp,mx.tmp,NE.tmp,vpa.tmp,mr.tmp,am.tmp,Stocks,ASR_stocks,ASR_long,file = "D:/Github/ICM/Results/model_inputs.Rdata")

@@

load(file = "D:/Github/ICM/Results/model_inputs.Rdata")

@@

  tst <- back.sim(years,
                 mat.age = age.mat,
                 nm = -(log(1-prop.nat.mort)),
                 w.age = weight.age,
                 ages = ages,
                 rems = rem$rem,
                 fecund = mx,
                 N.end = N.end,
                 pop.model = 'exponential',
                 n.sims = 500,
                 sd.mat = 0.5,
                 sd.nm = 0.5,
                 sd.wt = 0.5,
                 sd.fecund = 0.5)

@@

# ########################## Now run the tuning sims
#
   N.end <- vpa.abund[length(vpa.abund)]
   tunes <- tune.sim(years,
                     n.steps = 100,
                     abund.ts = vpa.abund,
                     mat.age = age.mat,
                     nm = -(log(1-prop.nat.mort)),
                     w.age = weight.age,
                     ages = ages,
                     rems = rem$rem,
                     fecund = mx,
                     N.end = N.end,
                     pop.model = 'exponential')

   tuned.res[[i]] <- tunes
} # end i in Stocks look

# Save all these
 saveRDS(object = tuned.res,file = "D:/Github/ICM/Results/tuned_fits.Rds")
 saveRDS(object = back.res,file = "D:/Github/ICM/Results/backwards_sim_results.Rds")
 saveRDS(object = back.ts,file = "D:/Github/ICM/Results/backwards_sim_ts_summaries.Rds")
 saveRDS(object = back.ts.quants,file = "D:/Github/ICM/Results/backwards_sim_ts_quantiles_summaries.Rds")
```

>>>>

```{r, load-stuff,echo=F, message=F, warning=F, fig.width=6, fig.height=4}
# OK, so using the ICES assessments here's what we get for North Sea cod.
library(readxl)
library(tidyverse)
library(rio)
library(ggthemes)
library(cowplot)
loc <- 'C:/Users/Owner/Documents/GitHub/ICM'

source(paste0(loc,"/Scripts/functions/backwards_sim.R"))
source(paste0(loc,"/Scripts/functions/tuning_sim.R"))

# Choose 5 ICES stocks that we have the necessary data for
#ASR <- read_xlsx("../Data/ASR_2018.xlsx" sheet = "ICES")
ASR1 <- read.csv(paste0(loc,"/Data/ICM_data_NE_atlantic_stocks.csv"))
ASR <- read.csv(paste0(loc,"/Data/ICM_data_NW_atlantic_stocks.csv"))

@@

  age.mat <- ASR_sub %>% dplyr::filter(type=="AM") %>% dplyr::rename(AM=value) %>% dplyr::select(-type)
  # All of the age at maturities are NA in 0 and 1 year olds, so make them 0's, do that carefully just
  # in case that changes later...
  am.0s <- length(which((!is.na(age.mat$AM[age.mat$age ==0]))))
  am.1s <- length(which((!is.na(age.mat$AM[age.mat$age ==1]))))
  am.2s <- length(which((!is.na(age.mat$AM[age.mat$age ==2]))))
  if(am.0s == 0) age.mat$AM[age.mat$age ==0] <- 0
  if(am.1s == 0) age.mat$AM[age.mat$age ==1] <- 0
  if(am.2s == 0) age.mat$AM[age.mat$age ==2] <- 0

  #if(am.1s | am.0s | am.2s > 0) print("Stop, you need to check the age at maturity for either age 0 or 1 as there is data in there.")
  nat.mort <-  ASR_sub %>% dplyr::filter(type=="NM") %>% dplyr::rename(NM=value) %>% dplyr::select(-type)
  abund <- ASR_sub %>% dplyr::filter(type=="Num") %>% dplyr::rename(Num=value) %>% dplyr::select(-type)
  weight.age <- ASR_sub %>% dplyr::filter(type=="WA") %>% dplyr::rename(WA=value) %>% dplyr::select(-type)
  removals <- ASR_sub %>% dplyr::filter(type=="Catch") %>% dplyr::rename(Catch=value) %>% dplyr::select(-type)

@@

  # Aahh??  Is this NA dropping useful data, needed to quick fix the age at maturity data...
  data$available <- apply(is.na(data[, c("AM", "Num", "WA")]), 1, function(x) all(!x==T))
  data <- data[data$available==T,]

@@

save(years.tmp,pnm.tmp,waa.tmp,ages.tmp,rem.tmp,mx.tmp,NE.tmp,vpa.tmp,mr.tmp,am.tmp,Stocks,ASR_stocks,ASR_long,file =  paste0(loc,"/Results/model_inputs.Rdata"))

@@

load(file = paste0(loc,"/Results/model_inputs.Rdata"))

@@

  tst <- back.sim(years,
                 mat.age = age.mat,
                 nm = -(log(1-prop.nat.mort)),
                 w.age = weight.age,
                 ages = ages,
                 rems = rem$rem,
                 fecund = mx,
                 N.end = N.end,
                 pop.model = 'exponential',
                 n.sims = 50,
                 sd.mat = 0.5,
                 sd.nm = 0.5,
                 sd.wt = 0.5,
                 sd.fecund = 0.5)

@@

# ########################## Now run the tuning sims
# #
#    N.end <- vpa.abund[length(vpa.abund)]
#    tunes <- tune.sim(years,
#                      n.steps = 100,
#                      abund.ts = vpa.abund,
#                      mat.age = age.mat,
#                      nm = -(log(1-prop.nat.mort)),
#                      w.age = weight.age,
#                      ages = ages,
#                      rems = rem$rem,
#                      fecund = mx,
#                      N.end = N.end,
#                      pop.model = 'exponential')
# 
#    tuned.res[[i]] <- tunes
} # end i in Stocks look

# Save all these
# saveRDS(object = tuned.res,file = "D:/Github/ICM/Results/tuned_fits.Rds")
 saveRDS(object = back.res,file = paste0(loc,"/Results/backwards_sim_results.Rds"))
 saveRDS(object = back.ts,file = paste0(loc,"/Results/backwards_sim_ts_summaries.Rds"))
 saveRDS(object = back.ts.quants,file = paste0(loc,"/Results/backwards_sim_ts_quantiles_summaries.Rds"))
```
